article title

### 2022-07-23 pilon_gilles_glossary.tex
Add type II error

>>>>

\newglossaryentry(type_ii_error},
    name={type II error},
    description={It is the probability of saying something is not different when in fact it is. We fail to find a difference when there is one. It is also called beta risk, consumer’s risk, and false negative. It is used to calculate the power of the test (1-beta), as well as in calculations of sample size.},
